---
title: "Case Study Setup"
output: html_document
date: "2023-12-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Generate Data

In this section, we will generate the data needed for the rest of the case study.
At the end of the file, we will also generate the first GLM to be used as our complement of credibility and append the prediction to this data.
We encourage you to save this data locally to avoid needing to resimulate it when proceeding with the case study.

First, we install the necessary packages for the case study.
A check for these packages is made at the beginning of future Rmd files, so no need to save this list for later.

```{r packages, echo=FALSE, include=FALSE}
# Function to install and load packages
install_and_load <- function(package) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
    library(package, character.only = TRUE)
  }
}

# List of packages
packages <- c("data.table", "statmod", "ggplot2", "tweedie", 
              "glmnet", "HDtweedie", "plotly", "arrow", "knitr")

# Install and load all packages
sapply(packages, install_and_load)

```

Now, we will define "true relativities" for variables in our base modeling dataset.
We are using an exponential shape to make it easy for our variable transformations to exactly match the true relativities.

```{r, echo=FALSE, include=FALSE}

driver_age_table <- data.table(
  "driver_age" = 18:100,
  "true_driver_age_relativity" = c(1.05^(20:1), c((.9^(1 / 39))^(0:39)), .9 * (1.01^(1:23)))
)
vehicle_age_table <- data.table(
  "vehicle_age" = 0:19,
  "true_vehicle_age_relativity" = c(1.03^(10:0), 1.01^(-1:-9))
)
even_category_table <- data.table(
  "even_category" = 0:1, "true_MultiPolicy_relativity" = (c(1, .8)),
  "MultiPolicy" = c("multi_no", "multi_yes")
)
small_category_table <- data.table(
  "small_category" = 0:1, "true_xTreme_TurnSignal_relativity" = c(1, .2),
  "xTreme_TurnSignal" = c("xTreme_no", "xTreme_yes")
)
four_category_table <- data.table(
  "four_categories" = 0:3, "true_car_weight_relativity" = c(.7, 1, 1.2, 1.2),
  "car_weight" = c(
    "weight_heavy", "weight_medium",
    "weight_light", "weight_extra_light"
  )
)
ten_category_table <- data.table(
  "ten_categories" = 0:9, "true_industry_code_relativity" =
    c(1.3, .8, .5, 1, .9, 1.2, 1.5, .7, .6, 2),
  "industry_code" = c(
    "ind_health_care", "ind_retail", "ind_finance_and_insurance",
    "ind_education", "ind_fine_arts", "ind_food_services",
    "ind_construction", "ind_farming", "ind_real_estate",
    "ind_fireworks"
  )
)
```

This is the same process, but for the large state data.
Differences from the base modeling data are noted through comments in the code.

```{r, echo=FALSE, include=FALSE}


# In this large state, the driver age relativity is steeper in the beginning and flat in the end.
# 1.05^(20:1) changed to 1.07^(20:1)
large_state_driver_age_table <- data.table(
  "driver_age" = 18:100,
  "true_driver_age_relativity" = c(
    1.06^(20:1), c((.9^(1 / 39))^(0:39)),
    .9 * (1.003^(1:23))
  )
)

# vehicle age in this large state remains the same
large_state_vehicle_age_table <- data.table(
  "vehicle_age" = 0:19,
  "true_vehicle_age_relativity" = c(1.03^(10:0), 1.01^(-1:-9))
)

# Multi-Policy Discount has a slightly larger discount here.
# Discount changed from .8 to .75
large_state_even_category_table <- data.table(
  "even_category" = 0:1, "true_MultiPolicy_relativity" = (c(1, .7)),
  "MultiPolicy" = c("multi_no", "multi_yes")
)

# people are using the xTreme TurnSignal slightly less effectively in this state
# discount changed from .2 to .4
large_state_small_category_table <- data.table(
  "small_category" = 0:1, "true_xTreme_TurnSignal_relativity" = c(1, .4),
  "xTreme_TurnSignal" = c("xTreme_no", "xTreme_yes")
)

# Light trucks have a better relativity, and extra_light cars perform much worse in this state
# 1.2 to 1.15, 1.2 to 1.3
large_state_four_category_table <- data.table(
  "four_categories" = 0:3, "true_car_weight_relativity" =
    c(.7, 1, 1.15, 1.3),
  "car_weight" = c(
    "weight_heavy", "weight_medium",
    "weight_light", "weight_extra_light"
  )
)

# Health Care performs better 1.3 to 1.2
# Fireworks performs even worse 2 to 2.5
# Construction performs better 1.5 to 1.4
large_state_ten_category_table <- data.table(
  "ten_categories" = 0:9, "true_industry_code_relativity" =
    c(1.2, .8, .5, 1, .9, 1.2, 1.4, .7, .6, 3),
  "industry_code" = c(
    "ind_health_care", "ind_retail",
    "ind_finance_and_insurance",
    "ind_education", "ind_fine_arts",
    "ind_food_services", "ind_construction",
    "ind_farming", "ind_real_estate",
    "ind_fireworks"
  )
)

```

This is the same process, but for the medium state data.
Differences from the base modeling data are noted through comments in the code.

```{r medium-state, echo=FALSE, include=FALSE}

# In this medium state, the driver age relativity is less steep in the beginning and decreases in the end.
# 1.05^(20:1) changed to 1.03^(20:1)
# 1.01^(1:23) changed to 1.01^(-1:-23)
medium_state_driver_age_table <- data.table(
  "driver_age" = 18:100,
  "true_driver_age_relativity" = c(
    1.03^(20:1), c((.9^(1 / 39))^(0:39)),
    .9 * (1.01^(-1:-23))
  )
)

# vehicle age in this medium state decreases faster in the tail
# 1.01^(-1:-9) changed to
medium_state_vehicle_age_table <- data.table(
  "vehicle_age" = 0:19,
  "true_vehicle_age_relativity" = c(1.03^(10:0), 1.02^(-1:-9))
)

# Multi-Policy Discount has a slightly smaller discount here.
# Discount changed from .8 to .75
medium_state_even_category_table <- data.table(
  "even_category" = 0:1, "true_MultiPolicy_relativity" = (c(1, .75)),
  "MultiPolicy" = c("multi_no", "multi_yes")
)

# people are using the xTreme TurnSignal slightly less effectively in this state
# discount changed from .2 to .5
medium_state_small_category_table <- data.table(
  "small_category" = 0:1, "true_xTreme_TurnSignal_relativity" = c(1, .5),
  "xTreme_TurnSignal" = c("xTreme_no", "xTreme_yes")
)

# Light vehicles have a worse relativity, and extra_light vehicles perform worse as well
# 1.2 to 1.3, 1.2 to 1.4
medium_state_four_category_table <- data.table(
  "four_categories" = 0:3, "true_car_weight_relativity" =
    c(.7, 1, 1.3, 1.4),
  "car_weight" = c(
    "weight_heavy", "weight_medium",
    "weight_light", "weight_extra_light"
  )
)

# Retail performs better in this state .8 to .7
# Fireworks performs better 2 to 1.5
# Fine arts are riskier .9 to 1.1
medium_state_ten_category_table <- data.table(
  "ten_categories" = 0:9, "true_industry_code_relativity" =
    c(1.3, .7, .5, 1, 1.1, 1.2, 1.5, .7, .6, 1.5),
  "industry_code" = c(
    "ind_health_care", "ind_retail",
    "ind_finance_and_insurance",
    "ind_education", "ind_fine_arts",
    "ind_food_services", "ind_construction",
    "ind_farming", "ind_real_estate",
    "ind_fireworks"
  )
)

```

This is the same process, but for the first small state data.
Differences from the base modeling data are noted through comments in the code.

```{r small-state, echo=FALSE, include=FALSE}

# This small state is different than the countrywide data (Unlike the next small state)

# Continues to decrease in the tail
small_state_driver_age_table <- data.table(
  "driver_age" = 18:100,
  "true_driver_age_relativity" = c(1.05^(20:1), c((.9^(1 / 39))^(0:62)))
)

# Steeper Driver Age
small_state_vehicle_age_table <- data.table(
  "vehicle_age" = 0:19,
  "true_vehicle_age_relativity" = c(1.04^(10:0), 1.01^(-1:-9))
)

# Not as much of a discount for multi-policy category: yes
small_state_even_category_table <- data.table(
  "even_category" = 0:1, "true_MultiPolicy_relativity" = (c(1, .6)),
  "MultiPolicy" = c("multi_no", "multi_yes")
)

# Turn Signal is not as effective in this state.
small_state_small_category_table <- data.table(
  "small_category" = 0:1, "true_xTreme_TurnSignal_relativity" = c(1, .6),
  "xTreme_TurnSignal" = c("xTreme_no", "xTreme_yes")
)

# extra light is more risky.
# heavy is only slightly less risky.
small_state_four_category_table <- data.table(
  "four_categories" = 0:3, "true_car_weight_relativity" = c(.8, 1, 1.2, 2),
  "car_weight" = c(
    "weight_heavy", "weight_medium",
    "weight_light", "weight_extra_light"
  )
)

# health_care is at the 1.0 relativity
# Real estate is slightly more risky
# food services is slightly less risky
small_state_ten_category_table <- data.table(
  "ten_categories" = 0:9, "true_industry_code_relativity" =
    c(1.4, .8, .5, 1, .9, 1.1, 1.5, .7, .7, 2),
  "industry_code" = c(
    "ind_health_care", "ind_retail",
    "ind_finance_and_insurance",
    "ind_education", "ind_fine_arts",
    "ind_food_services", "ind_construction",
    "ind_farming", "ind_real_estate",
    "ind_fireworks"
  )
)

```

Let's create a chart to compare the state differences between the driver age factors (Figure 7.2)...

```{r driver age, include=FALSE}

driver_age_table
large_state_driver_age_table
medium_state_driver_age_table
small_state_driver_age_table

# Assuming you have the four tables: driver_age_table, large_state_driver_age_table, 
# medium_state_driver_age_table, small_state_driver_age_table

# Merging and renaming columns
merged_table <- merge(driver_age_table, large_state_driver_age_table, by = "driver_age")
names(merged_table)[names(merged_table) == "true_driver_age_relativity.y"] <- "large"
names(merged_table)[names(merged_table) == "true_driver_age_relativity.x"] <- "full"

merged_table <- merge(merged_table, medium_state_driver_age_table, by = "driver_age")
names(merged_table)[names(merged_table) == "true_driver_age_relativity"] <- "medium"

merged_table <- merge(merged_table, small_state_driver_age_table, by = "driver_age")
names(merged_table)[names(merged_table) == "true_driver_age_relativity"] <- "small"

# Plotting
library(ggplot2)

ggplot(merged_table, aes(x = driver_age)) + 
    geom_line(aes(y = full, colour = "Full")) +
    geom_line(aes(y = large, colour = "Large")) +
    geom_line(aes(y = medium, colour = "Medium")) +
    geom_line(aes(y = small, colour = "Small")) +
    labs(title = "Driver Age Relativity by State Size",
         x = "Driver Age", 
         y = "True Driver Age Relativity") +
    theme_minimal()


```

... and the vehicle age factors (Figure 7.3)...

```{r vehicle_age , include=FALSE}


# Assuming you have the four tables: driver_age_table, large_state_driver_age_table, 
# medium_state_driver_age_table, small_state_driver_age_table

# Merging and renaming columns
merged_table <- merge(vehicle_age_table, large_state_vehicle_age_table, by = "vehicle_age")
names(merged_table)[names(merged_table) == "true_vehicle_age_relativity.y"] <- "large"
names(merged_table)[names(merged_table) == "true_vehicle_age_relativity.x"] <- "full"

merged_table <- merge(merged_table, medium_state_vehicle_age_table, by = "vehicle_age")
names(merged_table)[names(merged_table) == "true_vehicle_age_relativity"] <- "medium"

merged_table <- merge(merged_table, small_state_vehicle_age_table, by = "vehicle_age")
names(merged_table)[names(merged_table) == "true_vehicle_age_relativity"] <- "small"

# Plotting
library(ggplot2)

ggplot(merged_table, aes(x = vehicle_age)) + 
    geom_line(aes(y = full, colour = "Full")) +
    geom_line(aes(y = large, colour = "Large")) +
    geom_line(aes(y = medium, colour = "Medium")) +
    geom_line(aes(y = small, colour = "Small")) +
    labs(title = "Driver Age Relativity by State Size",
         x = "Driver Age", 
         y = "True Driver Age Relativity") +
    theme_minimal()


```

... and the industry code factors (Figure 7.7.

```{r ten_category age, echo=FALSE, include=FALSE}

copied_ten_category_table <- copy(ten_category_table)
copied_ten_category_table[, ten_categories := NULL]

copied_large_state_ten_category_table <- copy(large_state_ten_category_table)
copied_large_state_ten_category_table[, ten_categories := NULL]

copied_medium_state_ten_category_table <- copy(medium_state_ten_category_table)
copied_medium_state_ten_category_table[, ten_categories := NULL]

copied_small_state_ten_category_table <- copy(small_state_ten_category_table)
copied_small_state_ten_category_table[, ten_categories := NULL]

# Assuming you have the four tables: ten_category_table, large_state_ten_category_table, 
# medium_state_ten_category_table, small_state_ten_category_table

# Merging and renaming columns
merged_table <- merge(copied_ten_category_table, copied_large_state_ten_category_table, by = "industry_code")
names(merged_table)[names(merged_table) == "true_industry_code_relativity.y"] <- "large"
names(merged_table)[names(merged_table) == "true_industry_code_relativity.x"] <- "full"

merged_table <- merge(merged_table, copied_medium_state_ten_category_table, by = "industry_code")
names(merged_table)[names(merged_table) == "true_industry_code_relativity"] <- "medium"

merged_table <- merge(merged_table, copied_small_state_ten_category_table, by = "industry_code")
names(merged_table)[names(merged_table) == "true_industry_code_relativity"] <- "small"

merged_table
```

We can start now simulating the data.
Here is where we set the seed for our data simulation.

First the base modeling data...

```{r large state, echo=FALSE}

# Set the size of the various modeling datasets
nrow_base_modeling_data <- 2500000
nrow_large_state_modeling_data <- 500000
nrow_medium_state_modeling_data <- 300000
nrow_small_state_modeling_data <- 100000
nrow_small_cw_dist_state_modeling_data <- 100000

# This seed will make the data reproducable and match the case study
set.seed(99999)

base_modeling_data <- data.table(
  "driver_age" = round(rbeta(nrow_base_modeling_data, 2, 3) * 95 + 14, 0),
  "vehicle_age" = round(rbeta(nrow_base_modeling_data, 2, 5) * 20, 0),
  "even_category" = round(rbeta(nrow_base_modeling_data, 3, 3), 0),
  "small_category" = round(rbeta(nrow_base_modeling_data, 2, 7), 0),
  "four_categories" = round(rbeta(nrow_base_modeling_data, 3, 4) * 3, 0),
  "ten_categories" = round(rbeta(nrow_base_modeling_data, 3, 6) * 10, 0),
  "noise_factor" = rbeta(nrow_base_modeling_data, 4, 5) + .5,
  "subset" = "base_data",
  "stratification" = sample.int(5, nrow_base_modeling_data, replace = TRUE),
  "loss_cost" = 500
)

base_modeling_data[driver_age > 100, driver_age := 100]
base_modeling_data[driver_age %in% c(14, 15), driver_age := 19]
base_modeling_data[driver_age %in% c(16, 17), driver_age := 18]

base_modeling_data[vehicle_age > 20, vehicle_age := 20]
#
# hist(round(rbeta(nrow_base_modeling_data,2,3)*86+14,0))
min(round(rbeta(nrow_base_modeling_data, 2, 3) * 95 + 14, 0))
max(round(rbeta(nrow_base_modeling_data, 2, 3) * 95 + 14, 0))
# Take a look at the base modeling data.
head(base_modeling_data)
nrow(base_modeling_data)


# Make a list to merge the tables together
base_factor_tables <- list(
  driver_age_table, vehicle_age_table,
  even_category_table, small_category_table,
  four_category_table, ten_category_table
)

# Merge the tables together using a for-loop.
for (table in base_factor_tables) {
  base_modeling_data <- merge.data.table(base_modeling_data, table, by = colnames(table)[1])
}
# check that they were merged correctly
head(base_modeling_data)
nrow(base_modeling_data)

```

... then large stat data ...

```{r, echo=FALSE, include=FALSE}

# Now, we will perform all of these same operations for a large state subset

large_state_modeling_data <- data.table(
  "driver_age" = round(rbeta(nrow_large_state_modeling_data, 2, 3) * 95 + 14, 0),
  "vehicle_age" = round(rbeta(nrow_large_state_modeling_data, 2, 5) * 25, 0),
  "even_category" = round(rbeta(nrow_large_state_modeling_data, 3, 3), 0),
  "small_category" = round(rbeta(nrow_large_state_modeling_data, 2, 7), 0),
  "four_categories" = round(rbeta(nrow_large_state_modeling_data, 3, 4) * 3, 0),
  "ten_categories" = round(rbeta(nrow_large_state_modeling_data, 3, 6) * 10, 0),
  "noise_factor" = rbeta(nrow_large_state_modeling_data, 4, 5) + .5,
  "subset" = "large_state",
  "stratification" = sample.int(5, nrow_large_state_modeling_data,
    replace = TRUE
  ),
  "loss_cost" = 800
)

large_state_modeling_data[driver_age > 100, driver_age := 100]
base_modeling_data[driver_age %in% c(14, 15), driver_age := 19]
base_modeling_data[driver_age %in% c(16, 17), driver_age := 18]
large_state_modeling_data[vehicle_age > 20, vehicle_age := 20]
head(large_state_modeling_data)

# Again, list and merge the tables
large_state_factor_tables <- list(
  large_state_driver_age_table, large_state_vehicle_age_table,
  large_state_even_category_table, large_state_small_category_table,
  large_state_four_category_table, large_state_ten_category_table
)

for (table in large_state_factor_tables) {
  large_state_modeling_data <- merge.data.table(large_state_modeling_data, table, by = colnames(table)[1])
}
head(large_state_modeling_data)
nrow(large_state_modeling_data)


```

... medium state data ...

```{r medium-gen, echo=FALSE, include=FALSE}
# Now, we will perform all of these same operations for a medium state subset

medium_state_modeling_data <- data.table(
  "driver_age" = round(rbeta(nrow_medium_state_modeling_data, 2, 3) * 95 + 14, 0),
  "vehicle_age" = round(rbeta(nrow_medium_state_modeling_data, 2, 5) * 25, 0),
  "even_category" = round(rbeta(nrow_medium_state_modeling_data, 3, 3), 0),
  "small_category" = round(rbeta(nrow_medium_state_modeling_data, 2, 7), 0),
  "four_categories" = round(rbeta(nrow_medium_state_modeling_data, 3, 4) * 3, 0),
  "ten_categories" = round(rbeta(nrow_medium_state_modeling_data, 3, 6) * 10, 0),
  "noise_factor" = rbeta(nrow_medium_state_modeling_data, 4, 5) + .5,
  "subset" = "medium_state",
  "stratification" = sample.int(5, nrow_medium_state_modeling_data,
    replace = TRUE
  ),
  "loss_cost" = 450
)

medium_state_modeling_data[driver_age > 100, driver_age := 100]
base_modeling_data[driver_age %in% c(14, 15), driver_age := 19]
base_modeling_data[driver_age %in% c(16, 17), driver_age := 18]
medium_state_modeling_data[vehicle_age > 20, vehicle_age := 20]

head(medium_state_modeling_data)


medium_state_factor_tables <- list(
  medium_state_driver_age_table, medium_state_vehicle_age_table,
  medium_state_even_category_table, medium_state_small_category_table,
  medium_state_four_category_table, medium_state_ten_category_table
)

for (table in medium_state_factor_tables) {
  medium_state_modeling_data <- merge.data.table(medium_state_modeling_data, table, by = colnames(table)[1])
}
head(medium_state_modeling_data)

```

... and small state data.

```{r small-state-gen, echo=FALSE, include=FALSE}

# Now, we will perform all of these same operations for a small state subset

small_state_modeling_data <- data.table(
  "driver_age" = round(rbeta(nrow_small_state_modeling_data, 2, 3) * 95 + 14, 0),
  "vehicle_age" = round(rbeta(nrow_small_state_modeling_data, 2, 5) * 25, 0),
  "even_category" = round(rbeta(nrow_small_state_modeling_data, 3, 3), 0),
  "small_category" = round(rbeta(nrow_small_state_modeling_data, 2, 7), 0),
  "four_categories" = round(rbeta(nrow_small_state_modeling_data, 3, 4) * 3, 0),
  "ten_categories" = round(rbeta(nrow_small_state_modeling_data, 3, 6) * 10, 0),
  "noise_factor" = rbeta(nrow_small_state_modeling_data, 4, 5) + .5,
  "subset" = "small_state",
  "stratification" = sample.int(5, nrow_small_state_modeling_data,
    replace = TRUE
  ),
  "loss_cost" = 400
)
small_state_modeling_data[driver_age > 100, driver_age := 100]
base_modeling_data[driver_age %in% c(14, 15), driver_age := 19]
base_modeling_data[driver_age %in% c(16, 17), driver_age := 18]
small_state_modeling_data[vehicle_age > 20, vehicle_age := 20]
head(small_state_modeling_data)


small_state_factor_tables <- list(
  small_state_driver_age_table, small_state_vehicle_age_table,
  small_state_even_category_table, small_state_small_category_table,
  small_state_four_category_table, small_state_ten_category_table
)

for (table in small_state_factor_tables) {
  small_state_modeling_data <- merge.data.table(small_state_modeling_data, table, by = colnames(table)[1])
}
head(small_state_modeling_data)


```

Additionally, let's generate a second small state data set with the same true risk relativities as the larger modeling data set.

```{r gen-small-state-2, echo=FALSE, include=FALSE}

# Now, we will perform all of these same operations for a small state subset.
# Here, all relativities are identical to our base_modeling_data subset

small_cw_dist_state_modeling_data <- data.table(
  "driver_age" = round(rbeta(nrow_small_cw_dist_state_modeling_data, 2, 3) * 95 + 14, 0),
  "vehicle_age" = round(rbeta(nrow_small_cw_dist_state_modeling_data, 2, 5) * 25, 0),
  "even_category" = round(rbeta(nrow_small_cw_dist_state_modeling_data, 3, 3), 0),
  "small_category" = round(rbeta(nrow_small_cw_dist_state_modeling_data, 2, 7), 0),
  "four_categories" = round(rbeta(nrow_small_cw_dist_state_modeling_data, 3, 4) * 3, 0),
  "ten_categories" = round(rbeta(nrow_small_cw_dist_state_modeling_data, 3, 6) * 10, 0),
  "noise_factor" = rbeta(nrow_small_cw_dist_state_modeling_data, 4, 5) + .5,
  "subset" = "small_cw_dist_state",
  "stratification" = sample.int(5, nrow_small_cw_dist_state_modeling_data, replace = TRUE),
  "loss_cost" = 500
)


small_cw_dist_state_modeling_data[driver_age > 100, driver_age := 100]
base_modeling_data[driver_age %in% c(14, 15), driver_age := 19]
base_modeling_data[driver_age %in% c(16, 17), driver_age := 18]
small_cw_dist_state_modeling_data[vehicle_age > 20, vehicle_age := 20]

# This small state is identical to the base modeling data

small_cw_dist_state_driver_age_table <- data.table(
  "driver_age" = 18:100,
  "true_driver_age_relativity" = c(
    1.05^(20:1),
    c((.9^(1 / 39))^(0:39)),
    .9 * (1.01^(1:23))
  )
)

small_cw_dist_state_vehicle_age_table <- data.table(
  "vehicle_age" = 0:19,
  "true_vehicle_age_relativity" = c(1.03^(10:0), 1.015^(-1:-9))
)

small_cw_dist_state_even_category_table <- data.table(
  "even_category" = 0:1,
  "true_MultiPolicy_relativity" = (c(1, .8)),
  "MultiPolicy" = c("multi_no", "multi_yes")
)

small_cw_dist_state_small_category_table <- data.table(
  "small_category" = 0:1,
  "true_xTreme_TurnSignal_relativity" = c(1, .2),
  "xTreme_TurnSignal" = c("xTreme_no", "xTreme_yes")
)

small_cw_dist_state_four_category_table <- data.table(
  "four_categories" = 0:3,
  "true_car_weight_relativity" = c(.7, 1, 1.2, 1.2),
  "car_weight" = c(
    "weight_heavy", "weight_medium",
    "weight_light", "weight_extra_light"
  )
)

small_cw_dist_state_ten_category_table <- data.table(
  "ten_categories" = 0:9, "true_industry_code_relativity" =
    c(1.3, .8, .5, 1, .9, 1.2, 1.5, .7, .6, 2),
  "industry_code" = c(
    "ind_health_care", "ind_retail",
    "ind_finance_and_insurance",
    "ind_education", "ind_fine_arts",
    "ind_food_services", "ind_construction",
    "ind_farming", "ind_real_estate",
    "ind_fireworks"
  )
)

small_cw_dist_state_factor_tables <- list(
  small_cw_dist_state_driver_age_table,
  small_cw_dist_state_vehicle_age_table,
  small_cw_dist_state_even_category_table,
  small_cw_dist_state_small_category_table,
  small_cw_dist_state_four_category_table,
  small_cw_dist_state_ten_category_table
)

for (table in small_cw_dist_state_factor_tables) {
  small_cw_dist_state_modeling_data <- merge.data.table(small_cw_dist_state_modeling_data, table, by = colnames(table)[1])
}

# Create the final overall modeling dataset
modeling_data <- rbind(
  base_modeling_data,
  large_state_modeling_data,
  medium_state_modeling_data,
  small_state_modeling_data,
  small_cw_dist_state_modeling_data
)




```

We now have a full modeling dataset with all of the characteristics and true risk relativities.
It is now time to compute the overall true risk (as multiplication of relativities and loss cost) and proceed to simulate incurred losses using a tweedie distribution.

```{r, echo=FALSE, include=FALSE}
#### 2. Create variable transformations for modeling ####

# set base levels for categorical variables
modeling_data[, industry_code := relevel(as.factor(industry_code), ref = "ind_education")]
modeling_data[, car_weight := relevel(as.factor(car_weight), ref = "weight_medium")]
modeling_data[, xTreme_TurnSignal := relevel(as.factor(xTreme_TurnSignal), ref = "xTreme_no")]
modeling_data[, MultiPolicy := relevel(as.factor(MultiPolicy), ref = "multi_no")]
modeling_data[, subset := relevel(as.factor(subset), ref = "base_data")]


# calculate true risk multiplicatively to match the selected link function
modeling_data[, "true_risk" := loss_cost * true_driver_age_relativity * true_vehicle_age_relativity *
  true_MultiPolicy_relativity * true_xTreme_TurnSignal_relativity *
  true_car_weight_relativity * true_industry_code_relativity]

# Simulate the incurred loss using the true risk value
# Note that an error term is not included in this calculation
# You could include this in a "true_risk_with_error" column to simulate a dataset with additional volatility
modeling_data[, "incurred_loss" := rtweedie(length(true_risk), mu = true_risk, phi = 800, power = 1.6)]

# See that the overall frequency is about 4%.
# This frequency is an item that may be adjusted in future iterations
nrow(modeling_data[incurred_loss != 0, ]) / nrow(modeling_data)

# Average Risk is a bit under 700
mean(modeling_data$true_risk)

# We can see that the means are close, but as expected, there are far more zero values in the incurred_loss
summary(modeling_data$incurred_loss)
summary(modeling_data$true_risk)

# To simplify this case study, all exposures will be one. If this is set to a different value, our incurred_loss would need to be recalculated to reflect the fact that the true risk would be lower for partial policy terms.

modeling_data[, "exposure" := 1]
```

Because we know the true distribution of risk in the underlying dataset, we can use the "perfect" feature engineering in each model.
We will use this for our

This simplification is necessary to focus on the behavior of lasso credibility and not the individual feature engineering of each model.
It is true that this is not the best feature engeineering for each model because models describe the data - they do not describe the truth.
However, for the sake of this case study, we will use these transformations.

Models using iterative feature engineering are never "done" - we can likely always find a slightly statistically better feature engineering through iteration.
This simplifying assumption will allow us to focus on the behavior of lasso credibility rather than this iterative process.
Also, we will not introduce human error into this comparison by spending more time perfecting the feature engineering of one model vs. another.

```{r hinges}

# Create modeling hinges for driver_age
modeling_data[, driver_age_18_38_hinge := pmin(driver_age, 38)]
modeling_data[, driver_age_38_76_hinge := pmin(pmax(driver_age, 38), 76)]
modeling_data[, driver_age_76_99_hinge := pmax(driver_age, 76)]

#summary(modeling_data$driver_age_18_38_hinge)
#summary(modeling_data$driver_age_38_76_hinge)
#summary(modeling_data$driver_age_76_99_hinge)

# Create modeling hinges for vehicle_age
modeling_data[, vehicle_age_0_10_hinge := pmin(vehicle_age, 10)]
modeling_data[, vehicle_age_10_99_hinge := pmax(vehicle_age, 10)]

table(modeling_data$vehicle_age_0_10_hinge)
table(modeling_data$vehicle_age_10_99_hinge)

#summary(modeling_data$vehicle_age_0_10_hinge)
#summary(modeling_data$vehicle_age_10_99_hinge)


# Create one-hot encoded versions of categorical variables for penalized regression.
# We will do this manually for clarity. There are more efficient ways to code this.
# We will NOT create a one-hot level for the most populated variable.
# If we included all levels of a categorical variable as one-hot encoded, it would create aliasing.

# For the first two categorical variables, we already have the binary one-hot in our dataset.
modeling_data[, multi_yes := even_category]
modeling_data[, xTreme_yes := small_category]

# For the others, we will identify the base level, and then not include that in our one-hot variables
table(modeling_data$car_weight) # Medium is the base level

modeling_data[, weight_heavy := ifelse(car_weight == "weight_heavy", 1, 0)]
modeling_data[, weight_light := ifelse(car_weight == "weight_light", 1, 0)]
modeling_data[, weight_extra_light := ifelse(car_weight == "weight_extra_light", 1, 0)]

# Same procedure for the ten category variable "industry_code"
table(modeling_data$industry_code) # Education is the base level

modeling_data[, ind_construction := ifelse(industry_code == "ind_construction", 1, 0)]
modeling_data[, ind_farming := ifelse(industry_code == "ind_farming", 1, 0)]
modeling_data[, ind_finance_and_insurance := ifelse(industry_code == "ind_finance_and_insurance", 1, 0)]
modeling_data[, ind_fine_arts := ifelse(industry_code == "ind_fine_arts", 1, 0)]
modeling_data[, ind_fireworks := ifelse(industry_code == "ind_fireworks", 1, 0)]
modeling_data[, ind_food_services := ifelse(industry_code == "ind_food_services", 1, 0)]
modeling_data[, ind_health_care := ifelse(industry_code == "ind_health_care", 1, 0)]
modeling_data[, ind_real_estate := ifelse(industry_code == "ind_real_estate", 1, 0)]
modeling_data[, ind_retail := ifelse(industry_code == "ind_retail", 1, 0)]
modeling_data[, ind_base_data := ifelse(subset == "base_data", 1, 0)]
modeling_data[, ind_large_state := ifelse(subset == "large_state", 1, 0)]
modeling_data[, ind_medium_state := ifelse(subset == "medium_state", 1, 0)]
modeling_data[, ind_small_state := ifelse(subset == "small_state", 1, 0)]
modeling_data[, ind_small_state_cw_dist := ifelse(subset == "small_cw_dist_state", 1, 0)]

# set base levels and change to factors for GLM modeling.
modeling_data[, industry_code := relevel(as.factor(industry_code), ref = "ind_education")]
modeling_data[, car_weight := relevel(as.factor(car_weight), ref = "weight_medium")]
modeling_data[, xTreme_TurnSignal := relevel(as.factor(xTreme_TurnSignal), ref = "xTreme_no")]
modeling_data[, MultiPolicy := relevel(as.factor(MultiPolicy), ref = "multi_no")]
modeling_data[, subset := relevel(as.factor(subset), ref = "base_data")]
```

For the purpose of reproduction we also fit the countrywide model (will be discussed in a separate Rmd file).
This model's score is appended to the data to be used as a complement of credibility for future models.

```{r fitcountrywide}

training_data <- modeling_data[stratification %in% c(1, 2, 3, 4), ]

# run our initial GLM model
glm_model <- glm(
  formula = incurred_loss ~
    driver_age_18_38_hinge + driver_age_38_76_hinge + driver_age_76_99_hinge +
    vehicle_age_0_10_hinge + vehicle_age_10_99_hinge +
    C(MultiPolicy) + C(xTreme_TurnSignal) + C(car_weight) + C(industry_code) + C(subset),
  family = tweedie(1.6, link.power = 0),
  offset = log(exposure),
  data = training_data
)


modeling_data[, cw_model_complement_of_credibility := predict.glm(glm_model, modeling_data, type = "response")]

```

And we finally export it.
Change the working directory here as you want.

```{r export, echo=FALSE, include=FALSE}

getwd()
#setwd()
# Write to Parquet file
write_parquet(modeling_data, "output_file.parquet")

```

```{r}



```
