---
title: "Small State Analysis"
output: html_document
date: "2023-12-28"
---


Small State Model: GLM vs Lasso Credibility

This markdown is intended to be run after the countrywide, large, and medium state analysis so that the data needed are still in our environment. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in packages as needed

```{r packages, echo=FALSE, include=FALSE}
# Function to install and load packages
install_and_load <- function(package) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
    library(package, character.only = TRUE)
  }
}

# List of packages
packages <- c("data.table", "statmod", "ggplot2", "tweedie", 
              "glmnet", "HDtweedie", "plotly", "arrow", "knitr")

# Install and load all packages
sapply(packages, install_and_load)
```

Read in helper functions

```{r echo=FALSE, include=FALSE}
source( "helper_functions.R")
```

Read in the data as needed

```{r pressure, echo=FALSE, include=FALSE}
modeling_data <- read_parquet("output_file.parquet")

```

Prepare to model the small state data

```{r, echo=FALSE, include=FALSE}

# Subset the modeling_data table
subset_data <- modeling_data[subset == "base_data", ]
# Convert the data.table to a data.frame
subset_df <- as.data.frame(subset_data)
# Write the subset_df as a Parquet file


# filter to training rows only
training_data <- modeling_data[stratification %in% c(1, 2, 3, 4), ]

# select modeling variables for Lasso
lasso_modeling_variables <- c(
  "driver_age_18_38_hinge", "driver_age_38_76_hinge", "driver_age_76_99_hinge",
  "vehicle_age_0_10_hinge", "vehicle_age_10_99_hinge",
  "multi_yes", "xTreme_yes",
  "weight_heavy", "weight_light", "weight_extra_light",
  "ind_construction", "ind_farming", "ind_finance_and_insurance",
  "ind_fine_arts", "ind_fireworks", "ind_food_services",
  "ind_health_care", "ind_real_estate", "ind_retail",
  "ind_large_state", "ind_medium_state",
  "ind_small_state", "ind_small_state_cw_dist"
)

# HDTweedie requires a matrix format for predictor variables. First, we will subset to all of the columns that we need.
train_cols_for_matrix <- modeling_data[stratification %in% c(1, 2, 3, 4), lasso_modeling_variables, with = FALSE]
validate_cols_for_matrix <- modeling_data[stratification %in% c(5), lasso_modeling_variables, with = FALSE]

# Reformatting to a matrix for HDtweedie so that Lasso Tweedie can work.
training_data_matrix <- as.matrix(train_cols_for_matrix, rownames = FALSE)
validate_data_matrix <- as.matrix(validate_cols_for_matrix, rownames = FALSE)

# This is the data format needed for creating our loss vector and CV vector below
training_data <- modeling_data[stratification %in% c(1, 2, 3, 4), ]
validate_data <- modeling_data[stratification %in% c(5), ]

# Losses and CV need to be a vector
loss_vector <- as.vector(training_data$incurred_loss)
cv_vector <- as.vector(training_data$stratification)

# As exposures are all 1, we will create this vector.
weights <- rep(1, length(drop(loss_vector)))

```

Fit lasso credibility and GLM models

```{r, echo=FALSE, include=FALSE}
# We no longer need the state control variable
lasso_modeling_variables <- lasso_modeling_variables[!(lasso_modeling_variables %in% c("ind_small_state", "ind_base_data", "ind_medium_state", "ind_large_state", "ind_small_state_cw_dist"))]



#### Small State Model ####

small_state_training_data <- training_data[subset == "small_state"]
small_state_validate_data <- validate_data[subset == "small_state"]

cw_model_complement_of_credibility_vector <- small_state_training_data$cw_model_complement_of_credibility


# This is the data format needed for HDtweedie.
small_state_train_cols_for_matrix <- small_state_training_data[, lasso_modeling_variables, with = FALSE]
small_state_validate_cols_for_matrix <- small_state_validate_data[, lasso_modeling_variables, with = FALSE]

# Reformatting to a matrix for HDtweedie so that Lasso Tweedie can work.
small_state_training_data_matrix <- as.matrix(small_state_train_cols_for_matrix, rownames = FALSE)
small_state_validate_data_matrix <- as.matrix(small_state_validate_cols_for_matrix, rownames = FALSE)

# Losses and CV need to be a vector
small_state_training_loss_vector <- as.vector(small_state_training_data$incurred_loss)
small_state_training_cv_vector <- as.vector(small_state_training_data$stratification)

# fit the lasso model with an offset

recompute <- TRUE

if (recompute) {

small_state_offset_lasso_model <- cv.HDtweedie(
  x = small_state_training_data_matrix,
  y = (small_state_training_loss_vector * (cw_model_complement_of_credibility_vector^(1 - 1.6)) / (cw_model_complement_of_credibility_vector^(2 - 1.6))),
  group = NULL, p = 1.6,
  weights = small_state_training_data$exposure * (cw_model_complement_of_credibility_vector^(2 - 1.6)), lambda = NULL,
  pred.loss = "deviance",
  nfolds = 4, foldid = small_state_training_cv_vector,
  standardize = TRUE
)
saveRDS(small_state_offset_lasso_model, file = "small_state_offset_lasso_model.rds")
} else {
  medium_state_offset_lasso_model <- readRDS("small_state_offset_lasso_model.rds")
}

# fit the GLM model (without an offset)
small_state_glm_model <- glm(
  formula = incurred_loss ~
    driver_age_18_38_hinge + driver_age_38_76_hinge + driver_age_76_99_hinge +
    vehicle_age_0_10_hinge + vehicle_age_10_99_hinge +
    C(MultiPolicy) + C(xTreme_TurnSignal) + C(car_weight) + C(industry_code),
  family = tweedie(1.6, link.power = 0),
  weights = exposure,
  data = small_state_training_data
)

```


Show statistics of the glm. Note that many of these variables are insignificant. It would take significant work to make a reasonable model from this start. 

```{r}
summary(small_state_glm_model)
```


Show the CV plot for HDTweedie

```{r plot}

plot_lasso_model_cv_error(small_state_offset_lasso_model)

```

Now, we will compare the GLM vs. the Lasso with a complement of credibility


```{r small-state-comparison}

# add the predictions to our training data
small_state_training_data[, glm_prediction := predict.glm(small_state_glm_model, small_state_training_data, type = "response")]
small_state_training_data[, credibility_weighted_prediction := predict(small_state_offset_lasso_model, small_state_training_data_matrix,
  s = "lambda.min",
  weights = exposure
) * cw_model_complement_of_credibility]

small_state_validate_data[, glm_prediction := predict.glm(small_state_glm_model, small_state_validate_data, type = "response")]
small_state_validate_data[, credibility_weighted_prediction := predict(small_state_offset_lasso_model, small_state_validate_data_matrix,
  s = "lambda.min",
  weights = exposure
) * cw_model_complement_of_credibility]


small_state_credibility_coeff_table <- create_credibility_coeff_table(
  glm_model = small_state_glm_model,
  penalized_model = small_state_offset_lasso_model,
  complement_model = lasso_model
)
# Small Subset 1 GLM coefficients
capture.output(summary(small_state_glm_model))[c(13:36)]

# Small Subset 1 Credibility Coeff Table
summary(small_state_glm_model)
print(small_state_credibility_coeff_table)
write.csv(small_state_credibility_coeff_table, file = "../Graphs/SmallState/CSV/smallstate_coeff_table.csv", row.names = FALSE)


# Small Subset 1 MultiPolicy Discount
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "MultiPolicy"))

# Small Subset 1 xTreme Turn Signal Discount
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "xTreme_TurnSignal"))

# Small Subset 1 Industry Code
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "industry_code"))


# Additional Prediction and Relativity Plots
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "industry_code"))
credibility_prediction_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "industry_code"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "MultiPolicy"))
credibility_prediction_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "MultiPolicy"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_prediction_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "car_weight"))
credibility_prediction_plot(get_credibility_cat_var_table(small_state_training_data, small_state_credibility_coeff_table, "car_weight"))


small_state_driver_age_table <- get_credibility_driver_var_table(small_state_training_data, small_state_credibility_coeff_table, variable_name = "driver_age")
small_state_vehicle_age_table <- get_credibility_vehicle_var_table(small_state_training_data, small_state_credibility_coeff_table, variable_name = "vehicle_age")

credibility_relativity_plot(small_state_driver_age_table)
credibility_prediction_plot(small_state_driver_age_table)
credibility_relativity_plot(small_state_vehicle_age_table)
credibility_prediction_plot(small_state_vehicle_age_table)


# add the predictions to our holdout data and create charts
small_state_validate_data[, glm_prediction := predict.glm(small_state_glm_model, small_state_validate_data, type = "response")]
small_state_validate_data[, credibility_weighted_prediction := predict(small_state_offset_lasso_model, small_state_validate_data_matrix, s = "lambda.min") *
  small_state_validate_data$cw_model_complement_of_credibility]

print(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "industry_code"))

credibility_relativity_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "industry_code"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "MultiPolicy"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "car_weight"))

credibility_prediction_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "industry_code"))
credibility_prediction_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "MultiPolicy"))
credibility_prediction_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_prediction_plot(get_credibility_cat_var_table(small_state_validate_data, small_state_credibility_coeff_table, "car_weight"))


small_state_driver_age_table <- get_credibility_driver_var_table(small_state_validate_data, small_state_credibility_coeff_table, variable_name = "driver_age")
small_state_vehicle_age_table <- get_credibility_vehicle_var_table(small_state_validate_data, small_state_credibility_coeff_table, variable_name = "vehicle_age")


credibility_prediction_plot(small_state_driver_age_table)
credibility_prediction_plot(small_state_vehicle_age_table)


```

In the lift charts below, we can see that our lasso credibility model outperforms both the GLM and the countrywide model. However, this is not the most optimal model, as some of the univariate charts suggest that we should try a higher credibility standard. 

```{r small-state-double-lift}


## Small Data Lift Chart Lasso vs. GLM
# Figure 7.28
double_lift_chart(
  dataset = small_state_training_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "true_risk",
  normalize = TRUE
)




## Small Data Lift Chart Lasso vs. CW
# Figure 7.29
double_lift_chart(
  dataset = small_state_training_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "cw_model_complement_of_credibility",
  actual = "true_risk",
  normalize = TRUE
)



double_lift_chart(
  dataset = small_state_training_data,
  lasso_credibility = "cw_model_complement_of_credibility",
  glm = "glm_prediction",
  actual = "true_risk",
  normalize = TRUE
)


double_lift_chart(
  dataset = small_state_training_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "incurred_loss",
  normalize = TRUE
)

double_lift_chart(
  dataset = small_state_validate_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "true_risk",
  normalize = TRUE
)

double_lift_chart(
  dataset = small_state_validate_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "incurred_loss",
  normalize = TRUE
)

### Small State Increased Penalty Term ###
small_state_offset_lasso_model$lambda
small_state_offset_lasso_model$lambda.min


increased_penalty_coeff <- create_credibility_coeff_table_alternate_lambda(
  glm_model = small_state_glm_model,
  penalized_model = small_state_offset_lasso_model,
  complement_model = lasso_model,
  alternate_lambda = 1.374307155
)

print(increased_penalty_coeff)



small_state_training_data[, increased_penalty_prediction := predict(small_state_offset_lasso_model, small_state_training_data_matrix,
  s = 0.556990859,
  weights = exposure
) * cw_model_complement_of_credibility]

```

By applying actuarial judgment to increase our credibility standard, we arrive at a more actuarially sound model. 

```{r small-state-cw-increased-penalty}



# Increased Penalty Driver Age
credibility_relativity_plot(get_credibility_driver_var_table(small_state_training_data, increased_penalty_coeff, variable_name = "driver_age"))

# Increased Penalty Vehicle Age
credibility_relativity_plot(get_credibility_vehicle_var_table(small_state_training_data, increased_penalty_coeff, variable_name = "vehicle_age"))

# Increased Penalty Industry Code
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, increased_penalty_coeff, "industry_code"))

# Other plots for increased penalty model
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, increased_penalty_coeff, "MultiPolicy"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, increased_penalty_coeff, "xTreme_TurnSignal"))
credibility_relativity_plot(get_credibility_cat_var_table(small_state_training_data, increased_penalty_coeff, "car_weight"))


## Small State Increased Penalty vs. CW
# Figure 7.30
double_lift_chart(
  dataset = small_state_training_data,
  lasso_credibility = "increased_penalty_prediction",
  glm = "cw_model_complement_of_credibility",
  actual = "true_risk",
  normalize = TRUE
)


double_lift_chart(
  dataset = small_state_training_data,
  lasso_credibility = "increased_penalty_prediction",
  glm = "glm_prediction",
  actual = "true_risk",
  normalize = TRUE
)

selected_columns <- small_state_training_data[, c("increased_penalty_prediction", "cw_model_complement_of_credibility",
                                                  "glm_prediction", "credibility_weighted_prediction", "true_risk")]
write.csv(selected_columns, file = "../Graphs/SmallState/CSV/small_state_training_data_predictions.csv", row.names = FALSE)


```

We will fit our last models on the second small state subset which contains the same relativities as the base modeling data. 

```{r small-state-cw}

#### Small State with Base Modeling Data Relativities ###

small_cw_dist_state_training_data <- training_data[subset == "small_cw_dist_state"]
small_cw_dist_state_validate_data <- validate_data[subset == "small_cw_dist_state"]

cw_model_complement_of_credibility_vector <- small_cw_dist_state_training_data$cw_model_complement_of_credibility

# This is the data format needed for HDtweedie.
small_cw_dist_state_train_cols_for_matrix <- small_cw_dist_state_training_data[, lasso_modeling_variables, with = FALSE]
small_cw_dist_state_validate_cols_for_matrix <- small_cw_dist_state_validate_data[, lasso_modeling_variables, with = FALSE]

# Reformatting to a matrix for HDtweedie so that Lasso Tweedie can work.
small_cw_dist_state_training_data_matrix <- as.matrix(small_cw_dist_state_train_cols_for_matrix, rownames = FALSE)
small_cw_dist_state_validate_data_matrix <- as.matrix(small_cw_dist_state_validate_cols_for_matrix, rownames = FALSE)

# Losses and CV need to be a vector
small_cw_dist_state_training_loss_vector <- as.vector(small_cw_dist_state_training_data$incurred_loss)
small_cw_dist_state_training_cv_vector <- as.vector(small_cw_dist_state_training_data$stratification)

# fit the lasso model with an offset


recompute <- FALSE

if (recompute) {
small_cw_dist_state_offset_lasso_model <- cv.HDtweedie(
  x = small_cw_dist_state_training_data_matrix,
  y = (small_cw_dist_state_training_loss_vector * (cw_model_complement_of_credibility_vector^(1 - 1.6)) / (cw_model_complement_of_credibility_vector^(2 - 1.6))),
  group = NULL, p = 1.6,
  weights = small_cw_dist_state_training_data$exposure * (cw_model_complement_of_credibility_vector^(2 - 1.6)), lambda = NULL,
  pred.loss = "deviance",
  nfolds = 4, foldid = small_cw_dist_state_training_cv_vector,
  standardize = TRUE
)
  saveRDS(small_cw_dist_state_offset_lasso_model, file = "small_cw_dist_state_offset_lasso_model.rds")
} else {
  small_cw_dist_state_offset_lasso_model <- readRDS("lsmall_cw_dist_state_offset_lasso_model.rds")
}


# Fit the GLM model without an offset
small_cw_dist_state_glm_model <- glm(
  formula = incurred_loss ~
    driver_age_18_38_hinge + driver_age_38_76_hinge + driver_age_76_99_hinge +
    vehicle_age_0_10_hinge + vehicle_age_10_99_hinge +
    C(MultiPolicy) + C(xTreme_TurnSignal) + C(car_weight) + C(industry_code),
  family = tweedie(1.6, link.power = 0),
  weights = exposure,
  data = small_cw_dist_state_training_data
)



```

The charts below show that the optimal lasso credibility model has collapsed completely to the complement. All of the code to create additional graphs is provided for completeness and reusability. 

```{r comparison-sm}
# Now, we will compare the GLM vs. the Lasso with a complement of credibility

# add the predictions to our training data
small_cw_dist_state_training_data[, glm_prediction := predict.glm(small_cw_dist_state_glm_model, small_cw_dist_state_training_data, type = "response")]
small_cw_dist_state_training_data[, credibility_weighted_prediction := predict(small_cw_dist_state_offset_lasso_model, small_cw_dist_state_training_data_matrix,
  s = "lambda.min",
  weights = exposure
) * cw_model_complement_of_credibility]

small_cw_dist_state_validate_data[, glm_prediction := predict.glm(small_cw_dist_state_glm_model, small_cw_dist_state_validate_data, type = "response")]
small_cw_dist_state_validate_data[, credibility_weighted_prediction := predict(small_cw_dist_state_offset_lasso_model, small_cw_dist_state_validate_data_matrix,
  s = "lambda.min",
  weights = exposure
) * cw_model_complement_of_credibility]

small_cw_dist_state_credibility_coeff_table <- create_credibility_coeff_table(
  glm_model = small_cw_dist_state_glm_model,
  penalized_model = small_cw_dist_state_offset_lasso_model,
  complement_model = lasso_model
)

# Small Subset 2 GLM coefficients
capture.output(summary(small_cw_dist_state_glm_model))[c(13:36)]

# Small Subset 2 Credibility Coeff Table
print(small_cw_dist_state_credibility_coeff_table)
write.csv(small_cw_dist_state_credibility_coeff_table, file = "../Graphs/SmallState/CSV/smallstate_cw_dist_coeff_table.csv", row.names = FALSE)


credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "industry_code"))
credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "MultiPolicy"))
credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "car_weight"))

credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "industry_code"))
credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "MultiPolicy"))
credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "car_weight"))

small_cw_dist_state_driver_age_table <- get_credibility_driver_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, variable_name = "driver_age")
small_cw_dist_state_vehicle_age_table <- get_credibility_vehicle_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, variable_name = "vehicle_age")

credibility_relativity_plot(small_cw_dist_state_driver_age_table)
credibility_relativity_plot(small_cw_dist_state_vehicle_age_table)

credibility_prediction_plot(small_cw_dist_state_driver_age_table)
credibility_prediction_plot(small_cw_dist_state_vehicle_age_table)

write.csv(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "industry_code"), file = "../Graphs/SmallState/CSV/industry_code_cw_dist_table.csv", row.names = FALSE)
write.csv(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "MultiPolicy"), file = "../Graphs/SmallState/CSV/multipolicy_cw_dist_table.csv", row.names = FALSE)
write.csv(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "xTreme_TurnSignal"), file = "../Graphs/SmallState/CSV/xtreme_turnsignal_cw_dist_table.csv", row.names = FALSE)
write.csv(get_credibility_cat_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, "car_weight"), file = "../Graphs/SmallState/CSV/car_weight_cw_dist_table.csv", row.names = FALSE)
write.csv(get_credibility_driver_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, variable_name = "driver_age"), file = "../Graphs/SmallState/CSV/driver_age_cw_dist_table.csv", row.names = FALSE)
write.csv(get_credibility_vehicle_var_table(small_cw_dist_state_training_data, small_cw_dist_state_credibility_coeff_table, variable_name = "vehicle_age"), file = "../Graphs/SmallState/CSV/vehicle_age_cw_dist_table.csv", row.names = FALSE)


# add the predictions to our holdout data
small_cw_dist_state_validate_data[, glm_prediction := predict.glm(small_cw_dist_state_glm_model, small_cw_dist_state_validate_data, type = "response")]
small_cw_dist_state_validate_data[, credibility_weighted_prediction := predict(small_cw_dist_state_offset_lasso_model, small_cw_dist_state_validate_data_matrix, s = "lambda.min") *
  small_cw_dist_state_validate_data$cw_model_complement_of_credibility]


small_cw_dist_state_credibility_coeff_table <- create_credibility_coeff_table(
  glm_model = small_cw_dist_state_glm_model,
  penalized_model = small_cw_dist_state_offset_lasso_model,
  complement_model = lasso_model
)

print(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "industry_code"))

credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "industry_code"))
credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "MultiPolicy"))
credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_relativity_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "car_weight"))

credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "industry_code"))
credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "MultiPolicy"))
credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "xTreme_TurnSignal"))
credibility_prediction_plot(get_credibility_cat_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, "car_weight"))


small_cw_dist_state_driver_age_table <- get_credibility_driver_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, variable_name = "driver_age")
small_cw_dist_state_vehicle_age_table <- get_credibility_vehicle_var_table(small_cw_dist_state_validate_data, small_cw_dist_state_credibility_coeff_table, variable_name = "vehicle_age")


credibility_prediction_plot(small_cw_dist_state_driver_age_table)
credibility_prediction_plot(small_cw_dist_state_vehicle_age_table)

# Lift Charts
double_lift_chart(
  dataset = small_cw_dist_state_training_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "true_risk",
  normalize = TRUE
)

double_lift_chart(
  dataset = small_cw_dist_state_training_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "incurred_loss",
  normalize = TRUE
)

double_lift_chart(
  dataset = small_cw_dist_state_validate_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "true_risk",
  normalize = TRUE
)

double_lift_chart(
  dataset = small_cw_dist_state_validate_data,
  lasso_credibility = "credibility_weighted_prediction",
  glm = "glm_prediction",
  actual = "incurred_loss",
  normalize = TRUE
)

```


